\chapter{Continuum mechanics in different frames of reference}
All matter is made up of small building blocks called atoms, and the mathematics of the fundamental laws at this tiny scale is called quantum mechanics. The characteristic scales at which quantum mechanics operate is in the nanometer range, which is far smaller than most length scales found in nature.
If we zoom out to the \textit{macroscale}, the scale on which phenomena are large enough to be visible for the human eye, matter like solids and fluids behave statistically uniform, and it is reasonable to assume the matter can be mathematically described, and modeled, as a continuum. The continuum hypothesis states that there exist no space inside the matter and the matter completely fills up the space it occupies. 
We can use mathematics with basic Newtonian physical laws to model fluids and solids when they are assumed continuous. These newtonian laws are generally expressed in two frames of reference, Lagrangian and Eulerian, depending on the the scientific branch. \newline

To exemplify these frameworks we can imagine a river running down a mountain.	
In the Eulerian framework we are the observer standing besides the river looking at the flow. We are not interested in each fluid particle but only how the fluid acts as a whole flowing down the river. The Eulerian description of fluid mechanics is advantageous as we can imagine the fluid continuously deforming along the river side. \newline

The Lagrangian description is particularly beneficial for describing solid mechanical problems, as one is generally.

In the Lagrangian description we have to imagine ourselves on a leaf going down the river with the flow.  The Lagrangian description is particularly beneficial for describing solid mechanical problems, as one is generally interested in where the solid particles are in relation to each other. A solid mechanical example is modeling a deflecting beam attached to a wall. To model deflection one needs to know where all the particles are compared to each other. The more force that is applied the more the particles move in relation to each other. The Lagrangian description helps us to easier model a problem where need to know the particles spatial-relation to each other \newline

This chapter introduces briefly the fluid and solid equations with their respective boundary conditions. A detailed description of the Lagrangian framework and the stress and strain relations are covered in the appendix.

\input{./Solid_equations/Solid_equations}
\input{./Navier-Stokes/Navier-Stokes}
\input{./Continuum_mechanics/Boundary_conditions}


\begin{comment}
Let $\Omega \in \mathbb{R}^d $ for $d \in \{1,2\}$, be a bounded domain with boundary $ \partial \Omega$. The domain is made up of of two sub domains $ \mathcal{F} $ for the fluid domain, and $\mathcal{S}$ for the solid. The interface between the domains are denoted by $ \Sigma = \mathcal{F} \cap \mathcal{S} $. The reference or initial is denoted by $ \hat{\Sigma} = \hat{\mathcal{F}} \cap \hat{\mathcal{S}}  $ 
\end{comment}

